---
title: "HW-6"
format: html
editor: visual
---

Task 1: Conceptual Questions

---
#According to a source, the lapply() function returns a list of the same length as "x", each element of which is the result of applying 'FUN' to the "x".

#lapply(X, FUN, …)
---

```{r}
#lapply(cor(numeric_matrix, method = "kendall"))
```

```{r}
#Two advantages of using "purrr" functions as opposed to the "BaseR" apply family is that "purrr" functions provide an entire/complete and consistent group of tools for working with functions and tools. Additionally, another source states that "purr" functions have "consistent naming".

#SOURCES:
#https://purrr.tidyverse.org/ 
#https://purrr.tidyverse.org/articles/base.html
```

```{r}
# A side-effect function is a function that happens as a result of something, but however, is not returned.
```

```{r}
#You can name a variable "sd" in a function, and not cause any issues with the "sd" function, as long as you use the variable in different ways. 
```

Task 2 - Writing R Functions

```{r}
#set.seed(10)
#n <- 100
#x <- runif(n)
#resp <- 3 + 10 * x + rnorm(n)
#pred <- predict(lm(resp ~ x), data.frame(x))
```

```{r}
#getMRSE(resp, pred)
```

```{r}
#getMAE(resp, pred)
```

Let’s create a wrapper function that can be used to get either or both metrics returned with a single
function call. Do not rewrite your above two functions, call them inside the wrapper function (we
would call the getRMSE() and getMAE() functions helper functions). When returning your values,
give them appropriate names.
• The function should check that two numeric (atomic) vectors have been passed (consider is.vector(),
is.atomic(), and is.numeric()). If not, a message should print and the function should exit.
• The function should return both metrics by default and include names. The behavior should be able
to be changed using a character string of metrics to find.

```{r}
#wrapper <- function(getRMSE(), getMAE())
```

Task 3

```{r}
#install.packages('httr')
```

```{r}
#url <- httr::GET("https://newsapi.org/v2/everything?q=gamestop&from=2024-10-01&language=en&pageSize=100&apiKey=myKeyGoesHere")
```

```{r}
#purrr::pluck(url, articles)
```

```{r}
# Creating contingency table from vec using table()
#conTable = table(articles)
#print(conTable)
```

```{r}
#install.package("lubridate")
```

```{r}
#pub_diff <- lag(mutate(time))
```

```{r}
#map(pub_diff)
#map(publishedAt)
```
